### 2022-08-02 main/chapter_2ljets.tex
clarify specialized topother
kern all WZ

Additionally, $\twoljets$ widens its scope to target a GMSB simplified model
illustrated in Figure~\ref{fig:2ljets_signal_diagrams}.
The C1N2 and GMSB models behave similarly since both feature decays via massive
bosons ($WZ$, $ZZ$ or $Zh$) to leptons and jets, in similarly structures decay
trees to pairs of invisible supersymmetric particles.
Although widening sensitivity to both models does sacrifice sensitivity to
either one, the increased degree of model independence is itself of value for
future reinterpretations of the data.
We are happy to sacrifice some precision for generality.

@@

Some figures label CR-VZ as `CR-ZZ'; the region was renamed late in this
analysis project when it was show to contain substantial fractions of $WZ$
as well as $ZZ$, as illustrated in Figure~\ref{fig:2ljets_splits} of
Section~\ref{sec:2ljets_validation}.

@@

Since compressed signals generate softer kinematics and \atlas\ is sensitive
to soft leptons, three-lepton searches have stronger sensitivity to
compressed scenarios~\cite{atlas_rjr_3l_SUSY_2019_09}.
These searches consider the same C1N2 $WZ$ signal models as us, but target the
case where the $W$ decays leptonically $W\rightarrow\ell\nu$.
For comparison, impressive off-shell exclusion contours are reproduced
from the \atlas\ Run-2 $3\ell$ search~\cite{atlas_rjr_3l_SUSY_2019_09} in
Figure~\ref{fig:ljets_offshell_3l_exclusion}.

@@

Although it might be expected that our $Z$-like two-lepton selection would
favour the $ZZ$-like diboson sub-sample, with the other $Z$ decaying to
neutrinos,
Figure~\ref{fig:2ljets_splits_diboson} shows that in fact the three-lepton
$WZ$-like process has almost equal yields.
All of those $WZ$ events therefore have a missing third lepton, that could be
softer than the few $\eV[G]$ needed for our baseline selection
(see Section~\ref{sec:2ljets_events_leptons}),
or outside of our angular acceptance.
(Overlap removal cannot explain this since we count baseline leptons before
it.)
Although we would hope that such failed identifications would be rare,
the effect is enhanced by the fact that $WZ$ has a larger cross-section than
$ZZ$ by around a factor of three~\cite{Campbell:2011bn}, that is enhanced
by the sum over $W^+Z$ and $W^-Z$ processes.

@@

The remaining parts of Figure~\ref{fig:2ljets_splits_diboson} show that
of the rare-top sample, $\ttbar Z$ is the largest contribution,
at $73\%$ in \srllbb, but that contributions from other rare processes
such as $tW\kern-0.4exZ$, $t\ell\ell g$ and $\ttbar W$ are significant.
Here, the plain `Top other' label refers to all other rare-top contributions.

>>>>

Additionally, $\twoljets$ widens its scope to target a GMSB simplified model
illustrated in Figure~\ref{fig:2ljets_signal_diagrams}.
The C1N2 and GMSB models behave similarly since both feature decays via massive
bosons ($W\kern-0.4exZ$, $ZZ$ or $Zh$) to leptons and jets, in similarly structures decay
trees to pairs of invisible supersymmetric particles.
Although widening sensitivity to both models does sacrifice sensitivity to
either one, the increased degree of model independence is itself of value for
future reinterpretations of the data.
We are happy to sacrifice some precision for generality.

@@

Some figures label CR-VZ as `CR-ZZ'; the region was renamed late in this
analysis project when it was show to contain substantial fractions of $W\kern-0.4exZ$
as well as $ZZ$, as illustrated in Figure~\ref{fig:2ljets_splits} of
Section~\ref{sec:2ljets_validation}.

@@

Since compressed signals generate softer kinematics and \atlas\ is sensitive
to soft leptons, three-lepton searches have stronger sensitivity to
compressed scenarios~\cite{atlas_rjr_3l_SUSY_2019_09}.
These searches consider the same C1N2 $W\kern-0.4exZ$ signal models as us, but target the
case where the $W$ decays leptonically $W\rightarrow\ell\nu$.
For comparison, impressive off-shell exclusion contours are reproduced
from the \atlas\ Run-2 $3\ell$ search~\cite{atlas_rjr_3l_SUSY_2019_09} in
Figure~\ref{fig:ljets_offshell_3l_exclusion}.

@@

Although it might be expected that our $Z$-like two-lepton selection would
favour the $ZZ$-like diboson sub-sample, with the other $Z$ decaying to
neutrinos,
Figure~\ref{fig:2ljets_splits_diboson} shows that in fact the three-lepton
$W\kern-0.4exZ$-like process has almost equal yields.
All of those $W\kern-0.4exZ$ events therefore have a missing third lepton, that could be
softer than the few $\eV[G]$ needed for our baseline selection
(see Section~\ref{sec:2ljets_events_leptons}),
or outside of our angular acceptance.
(Overlap removal cannot explain this since we count baseline leptons before
it.)
Although we would hope that such failed identifications would be rare,
the effect is enhanced by the fact that $W\kern-0.4exZ$ has a larger cross-section than
$ZZ$ by around a factor of three~\cite{Campbell:2011bn}, that is enhanced
by the sum over $W^+\kern-0.4exZ$ and $W^-\kern-0.4exZ$ processes.

@@

The remaining parts of Figure~\ref{fig:2ljets_splits_diboson} show that
of the rare-top sample, $\ttbar Z$ is the largest contribution,
at $73\%$ in \srllbb, but that contributions from other rare processes
such as $tW\kern-0.4exZ$, $t\ell\ell g$ and $\ttbar W$ are significant.
Here, the plain `Top other' label refers to all other rare-top contributions
not included in the bracketed specializations.
